Challenges to transboundary fisheries management in North America under climate change

### 2019-10-25 Ecol_Manuscript_Draft.Rmd
Updates to manuscript

![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Results/Fig1.png)

@@

```{r Spatial_data, eval = T, echo = F, warning=F, message=F, results = 'hide'}

@@

![Fig 2. Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Results/Fig2.png)

@@

```{r IPHC_Map_Result_Regions, eval=T, echo=F}

@@

@@

```{r 4D_exploration, eval=F, echo=F,message=F, warning=F}

@@

```{r Figure_3, eval =F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC. A, RCP 2.6 represents a low emission scenario (high mitigation). B, RCP 8.5 represents a high emission scenario (status quo)"}

![Fig 3. Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Results/Fig3.png)

```{r IPHC_Proportion_Regions, eval=F, echo = F, message=F, warning=F}

```{r Figure_4, eval =F, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}

![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Results/Fig4.png)

```{r GB_Results_Spp, eval=F, echo = F, fig.width=12}

![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Results/Fig5.png)

```{r GB_Proportion_Species, eval =F, echo=F}
### Analysis by Species ####

![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Results/Fig6.png)

<!-- ## Species shifting towards the poles  -->

<!-- ## Uncertanty stuff -->

<!-- Discussion on improoving management  -->
<!-- From global (Cheung et al. 2016c) to regional (Morley et al. 2018) analysis, mitigating the effects of climate change will have positive results on fisheries (Sumaila 2019). In combination with improving management [Costello], fisheries will only be saved by a holistic approach… Indeed, dynamic management tools seem to work better than static strategies for resources expected to shift with changes in ocean condition (Pinsky and Selden 2017). -->

We ack

>>>>

![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Figures/Ecol//Fig1.png)

@@

```{r Spatial_data, eval = F, echo = F, warning=F, message=F, results = 'hide'}

@@

![Fig 2. Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Figures/Ecol/Fig2.png)

@@

```{r IPHC_Map_Result_Regions, eval = F, echo=F}

@@

```{r Figure_3, eval = F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC. A, RCP 2.6 represents a low emission scenario (high mitigation). B, RCP 8.5 represents a high emission scenario (status quo)"}

![Fig 3. Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Figures/Ecol/Fig3.png)

```{r IPHC_Proportion_Regions, eval = F, echo = F, message=F, warning=F}

```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}

![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Figures/Ecol/Fig4.png)

```{r GB_Results_Spp, eval = F, echo = F, fig.width=12}

```{r Figure_5, eval = T, echo =F, fig.cap="Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)"}

Fig4 <- readPNG("./Figures/Ecol/Fig5.png")
grid.raster(Fig5)

![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Figures/Ecol/Fig5.png)

```{r GB_Proportion_Species, eval = F, echo=F}
### Analysis by Species ####

```{r Figure_6, eval = T, echo =F, fig.cap="Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014"}

Fig4 <- readPNG("./Figures/Ecol/Fig6.png")
grid.raster(Fig5)

![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Figures/Ecol/Fig6.png)

<!-- # Old Analysis -->

<!-- ## Investigating 4D -->

@@

```{r 4D_exploration, eval = F, echo=F,message=F, warning=F}

@@
